Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex

\subsection{Tag Set Experiments}
We modified the tags for nouns (\texttt{subst}), verbs (\texttt{verb}),
adjectives (\texttt{adj}), determiners (\texttt{det}) and pronouns
(\texttt{pron}) in NDT by appending selected sets of morphological features to
each tag in order to increase the linguistic information expressed by the tags.
For each tag in turn, we first experiment with each of the available features in
isolation before testing various combinations in order to see how the features
might interact. We base our choices of combinations on how promising the
features are and what we deem worth investigating in terms of linguistic utility.

>>>>

\subsection{Tag Set Experiments}
We modify the tags for nouns (\texttt{subst}), verbs (\texttt{verb}),
adjectives (\texttt{adj}), determiners (\texttt{det}) and pronouns
(\texttt{pron}) in NDT by appending selected sets of morphological features to
each tag in order to increase the linguistic information expressed by the tags.
For each tag, we in turn first experiment with each of the available features in
isolation before testing various combinations. We base our choices
of combinations on how promising the features are and what we deem worth
For each tag, we first experiment with each of the available features in
isolation before employing various combinations of them. We base our choices of
combinations on how promising the features are and what we deem worth
investigating in terms of linguistic utility, in order to see how the features
might interact.
